Trial by Fire: Diachronic Regional Sentiment Towards American Wildfires

### 2022-12-12 paper.Rmd
minor edits

---
title: "Trial by Fire: Diachronic and Regional Sentiment Towards American Wildfires"
author: "Charles Hutchinson, Sam Kalman"
date: "December 12, 2022"
output: pdf_document
header-includes:
- \usepackage{booktabs}
- \usepackage{subfig}
- \usepackage{placeins}
---

@@

Lou, D & Camacho-Collados, J (2022).
“Cardiffnlp/Twitter-Roberta-Base-Sentiment-Latest · Hugging Face.” 
Huggingface.Co. \
(https://huggingface.co/cardiffnlp/twitter-roberta-base-sentiment-latest).

@@

### Please see submitted GitHub Repository for associated Code Appendix

>>>>

---
title: "Trial by Fire: Diachronic Regional Sentiment Towards American Wildfires"
author: "Charles Hutchinson, Sam Kalman"
date: "December 12, 2022"
output: pdf_document
header-includes:
- \usepackage{booktabs}
- \usepackage{subfig}
- \usepackage{placeins}
---

@@

Loureiro, D. et al. (2022).
“Cardiffnlp/Twitter-Roberta-Base-Sentiment-Latest · Hugging Face.” 
Huggingface.Co. \
(https://huggingface.co/cardiffnlp/twitter-roberta-base-sentiment-latest).

@@

## Code Appendix

Please find all code for this analysis at https://github.com/halseyhutch/wildfire_sentiment_analysis.
